Redshift Evolution of the Underlying Type Ia Supernova Stretch Distribution

### 2021-02-26 Nicolas.tex
2 columns and go
cleaned the usepackages, 1column useless now

\documentclass[referee]{aa}

\usepackage{txfonts}
\usepackage{ulem}
\usepackage{amsmath, mathtools}
\usepackage[colorlinks,breaklinks]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue}

@@

\def\l{\lambda}\def\L{\Lambda}

\newcommand{\nn}[1]{\textcolor[rgb]{1.0, 0.6, 0.0}{#1}}
\newcommand{\mr}[1]{\textcolor[rgb]{0.5, 0.20, 0.3}{#1}}
\newcommand{\yc}[1]{\textcolor[RGB]{217, 22, 102}{#1}}
\newcommand{\prob}[2]{\mathcal{P}\left( #1 \mid #2\right)}

@@

Type Ia supernovae (SNe Ia) are powerful cosmological distance indicators that
enabled the discovery of the acceleration of the Universe's expansion
\citep{riess1998, perlmutter1999}. They remain today a key cosmological probe to
understand the properties of dark energy (DE) as it is the only tool able to
precisely map the recent expansion rate ($z<0.5$), when DE is driving it
\citep[e.g.][]{scolnicastro2020}. They also are key to directly measure the
Hubble Constant ($H_0$), provided one can calibrate their absolute magnitude
\citep{riess2016, freedman2019}. Interestingly, the value of $H_0$ derived when
the SNe~Ia are anchored to Cepheids \citep[the SH0ES
project,][]{riess2009, riess2016} is $\sim5\sigma$ higher than what is predicted
from cosmic microwave background (CMB) data measured by Planck assuming the
standard $\L$CDM \citep{planck2018, riess2019, reid2019}, or when the SN
luminosity is anchored at intermediate redshift by the baryon acoustic
oscillation (BAO) scale \citep{feeney2019}. While using the tip of the red giant
branch technique in place of the Cepheids seem to favor an intermediate value of
$H_0$ \citep{freedman2019, freedman2020}, time delay measurements from strong
lensing seem to also favor high $H_0$ values \citep{wong2019}.

>>>>

\documentclass[]{aa}

\usepackage{txfonts}
\usepackage[colorlinks, breaklinks]{hyperref}
\hypersetup{linkcolor=blue, citecolor=blue, filecolor=black, urlcolor=blue}

@@

\newcommand{\prob}[2]{\mathcal{P}\left( #1 \mid #2\right)}

@@

Type Ia supernovae (SNe Ia) are powerful cosmological distance indicators that
enabled the discovery of the acceleration of the Universe's expansion
\citep{riess1998, perlmutter1999}. They remain today a key cosmological probe to
understand the properties of dark energy (DE) as it is the only tool able to
precisely map the recent expansion rate ($z<0.5$), when DE is driving it
\citep[e.g.][]{scolnicastro2020}. They also are key to directly measure the
Hubble Constant ($H_0$), provided one can calibrate their absolute magnitude
\citep{riess2016, freedman2019}. Interestingly, the value of $H_0$ derived when
the SNe~Ia are anchored to Cepheids \citep[the SH0ES
project,][]{riess2009, riess2016} is $\sim5\sigma$ higher than what is predicted
from cosmic microwave background (CMB) data measured by Planck assuming the
standard $\Lambda$CDM \citep{planck2018, riess2019, reid2019}, or when the SN
luminosity is anchored at intermediate redshift by the baryon acoustic
oscillation (BAO) scale \citep{feeney2019}. While using the tip of the red giant
branch technique in place of the Cepheids seem to favor an intermediate value of
$H_0$ \citep{freedman2019, freedman2020}, time delay measurements from strong
lensing seem to also favor high $H_0$ values \citep{wong2019}.
